Figures and tables for paper

### 2023-05-24 analysis/04_figs-tables.Rmd
Confirmed equivalence between HMNL and MNL draws for the dummy-coded experimental design

# Load packages, data, and draws

@@

# Load data
results <- read_rds(here("data", "derived_data", "final_data.rds"))

# Load draws
intercept <- 1                            # Intercept-only
interactions <- 0                         # Include interactions with the intercept-only model
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

```{r}
diff_cols <- function(col1, col2) {
  posterior_diffs <- draws %>% 
    filter(attribute %in% c({{col1}}, {{col2}})) %>% 
    select(.chain, .iteration, Theta, attribute) %>% 
    pivot_wider(names_from = "attribute", values_from = "Theta") %>% 
    mutate(diff_theta = .[[4]] - .[[3]],
           diff_theta_e = exp(.[[4]]) - exp(.[[3]]))

@@

>>>>

# Load packages and data

@@

# Load data
results <- read_rds(here("data", "derived_data", "final_data.rds"))
```

## Load draws

```{r hmnl-draws}
# Load draws
intercept <- 1                            # Intercept-only
interactions <- 0                         # Include interactions with the intercept-only model
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

```{r diff-function}
diff_cols <- function(col1, col2) {
  posterior_diffs <- draws %>% 
    filter(attribute %in% c({{col1}}, {{col2}})) %>% 
    select(.chain, .iteration, Theta, attribute) %>% 
    pivot_wider(names_from = "attribute", values_from = "Theta") %>% 
    mutate(diff_theta = .[[4]] - .[[3]],
           diff_theta_e = exp(.[[4]]) - exp(.[[3]]))

@@

## Plot MNL draws, experimental alternative

```{r plot-mnl-marginals}
################################################################################
# A flat MNL is an experimental alternative for dealing with interactions.
################################################################################

mnl_dummy_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl.rds"))
mnl_index_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl_index.rds"))

# Name levels labels
dummy_level_labels <- c(
  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
  str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
  str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
)

dummy_level_lookup <- tibble(levels = dummy_level_labels) %>%
  separate(levels, c("attribute", "level"), sep = ": ") %>%
  mutate(levels_long = paste0(attribute, ": ", level),
         i = 1:n()) %>%
  mutate_at(vars(attribute, level, levels_long), list(fct_inorder))

# Name levels labels (index-coded)
index_level_labels <- c(
  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
  str_c("Issue area: ", c("Emergency response", "Environment", "Human rights", "Refugee relief")),
  str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
  str_c("Funding sources: ", c("Many small private donations", "Handful of wealthy private donors", "Government grants")),
  str_c("Relationship with host government: ", c("Friendly", "Criticized", "Under crackdown"))
)

index_level_lookup <- tibble(levels = index_level_labels) %>%
  separate(levels, c("attribute", "level"), sep = ": ") %>%
  mutate(levels_long = paste0(attribute, ": ", level),
         i = 1:n()) %>%
  mutate_at(vars(attribute, level, levels_long), list(fct_inorder))

# Join level and covariate labels to draws
mnl_dummy_draws <- mnl_dummy_draws %>%
  rename(i = l) %>%
  left_join(dummy_level_lookup, by = "i")

mnl_index_draws <- mnl_index_draws %>%
  rename(i = l) %>%
  left_join(index_level_lookup, by = "i")

# Plot marginals.
mnl_dummy_draws %>%
  ggplot(aes(x = beta, y = levels_long)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Attribute Levels")

ggsave(
  "marginal-posteriors_mnl-intercept.png",
  path = here::here("analysis", "output", "figures"),
  width = width_length[1],
  height = width_length[2],
  units = "in"
)

mnl_index_draws %>%
  ggplot(aes(x = beta, y = levels_long)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Attribute Levels")
```
